Translation Elicitation: Report

### 2022-03-17 docs/index.Rmd
Add suggestions from @siowserene and refactor some code

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
    group_by(group) %>% 
    summarise_at(
        vars(frequency:lv), 
        list(
            mean = ~mean(., na.rm = TRUE),  
            sd = ~sd(., na.rm = TRUE)
        )
    ) %>%
    gt(rowname_col = "group") %>% 
    tab_header(
        title = md("Table 1"),
        subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
    ) %>% 
    tab_source_note(
        md("*Note*. Mean and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
    ) %>% 
    fmt_number(frequency_mean:pthn_sd) %>%
    fmt_percent(matches("lv")) %>% 
    tab_spanner(md("**Freq. (million)**"), c("frequency_mean", "frequency_sd")) %>% 
    tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
    tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
    tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
    cols_label(
        frequency_mean = md("Mean"),
        frequency_sd = md("*SD*"),
        frequency_zipf_mean = md("Mean"),
        frequency_zipf_sd = md("*SD*"),
        pthn_mean = md("Mean"),
        pthn_sd = md("*SD*"),
        lv_mean = md("Mean"),
        lv_sd = md("*SD*")
    ) %>% 
    summary_rows(
        columns = c(matches("mean"), -matches("lv")),
        fns = list(
            Mean = "mean",
            SD = "sd"
        )
    ) %>% 
    summary_rows(
        columns = matches("lv"),
        fns = list(
            Mean = "mean",
            SD = "sd"
        ), formatter = fmt_percent
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_stub_grand_summary()
    ) %>% 
    tab_style(
        style = cell_borders(sides = c("left", "right"), color = "white"),
        locations = list(
            cells_body(), cells_row_groups(), cells_column_spanners(), 
            cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
            cells_column_labels(), cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
        locations = cells_stub()
    ) %>% 
    tab_style(
        style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
        locations = list(cells_column_spanners(), cells_column_labels())
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:9)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:9)
    )

@@

participants_valid %>% 
    count(group, l2) %>% 
    mutate(
        l2 = case_when(
            l2=="Alemã\u0081n" ~ "German",
            l2=="Francã\u2030s" ~ "French",
            l2=="Cuã\u0081l" ~ "Missing",
            TRUE ~ l2
        ),
    ) %>% 
    left_join(count(participants_valid, group, name = "n_total")) %>% 
    mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
    ggplot(aes(group, n, fill = l2)) +
    facet_wrap(~group, ncol = 1, scales = "free_y") +
    geom_col(position = position_fill()) +
    labs(x = "L2", y = "# participants", fill = "L2") +
    scale_y_continuous(labels = percent) +
    coord_flip() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        strip.text = element_blank(),
        panel.grid = element_blank(),
        axis.text.x = element_text(angle = 90),
        axis.title.y = element_blank()
    )

@@

ggplot(post_re, aes(.value, reorder(as.factor(word), .value))) +
    geom_vline(xintercept = fixed_intercept[1], colour = "grey", size = 1) +

    stat_interval(
        size = 1.5,
        .width = c(0.5, 0.67, 0.95)
    ) +
    annotate(
        geom = "text",
        x = 0.7,
        y = 100,
        size = 3,
        hjust = 0.5,
        label = "Item accuracy \n(95%, 67%, and 50% CrI \nof item-level intercepts)"
    ) +
    annotate(
        geom = "rect",
        alpha = 0.15,
        xmin = fixed_intercept[2],
        xmax = fixed_intercept[3],
        ymin = -Inf,
        ymax = Inf
    ) +
    annotate(
        x = 0.7,
        xend = 0.6,
        y = 108,
        yend = 130,
        geom = "curve",
        curvature = 0.25,
        arrow = arrow(length = unit(0.2, "cm"))
    ) +
    annotate(
        geom = "text",
        x = 0.8,
        y = 10,
        size = 3,
        hjust = 0.5,
        label = "Global posterior accuracy\n(Mean ± 95% CrI of the \npopulation-level intercept)"
    ) +
    annotate(
        x = 0.7,
        xend = fixed_intercept[1]+0.05,
        y = 17,
        yend = 30,
        geom = "curve",
        curvature = 0.2,
        arrow = arrow(length = unit(0.2, "cm"))
    ) +
    labs(
        x = "Posterior probability of correct response",
        y = "Item",
        colour = "Credible Interval (CrI)",
        caption = "Credible intervals cover the range of values of the sampling space that \ncontain the true value with a given certainty."
    ) +
    scale_color_manual(
        values = c("#d2e5fc", "#9ccaff", "#1A85FF"),
        na.translate = FALSE, 
        labels = paste0(c(95, 67, 50), "%")
    ) +
    scale_x_continuous(limits = c(0, 1), labels = percent) +
    theme(
        legend.position = c(0.1, 0.9),
        legend.direction = "vertical",
        legend.justification = "left",
        legend.key = element_rect(fill = NA, colour = NA),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_text(size = 10),
        plot.caption.position = "plot",
        plot.caption = element_text(size = 9, hjust = 0, face = "plain", margin = margin(t = unit(3, "cm")))
    )

@@

@@

```{r emmeans_pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=7, fig.height=6}

m <- posterior_epreds_fixed %>% 
    mutate_at(vars(pthn_std, frequency_zipf_std), function(x) paste0(x, " SD")) %>% 
    mutate(
        pthn_std = case_when(
            pthn_std=="-1 SD" ~ "Low PTHN",
            pthn_std=="0 SD" ~ "Mean PTHN",
            pthn_std=="1 SD" ~ "High PTHN"
        ),
        frequency_zipf_std = case_when(
            frequency_zipf_std=="-1 SD" ~ "Low frequency",
            frequency_zipf_std=="0 SD" ~ "Mean frequency",
            frequency_zipf_std=="1 SD" ~ "High frequency"
        )
    )

ggplot(m, aes(lv_std, .epred, colour = pthn_std, fill = pthn_std)) +
    facet_wrap(~group) +
    geom_hline(yintercept = 0.5, colour = "grey") +
    geom_line(aes(group = interaction(pthn_std, .draw)), alpha = 0.25, size = 0.5, show.legend = TRUE) +
    stat_summary(aes(linetype = pthn_std), fun = mean, geom = "line", 
                 colour = "black", size = 0.75, show.legend = TRUE) +
    annotate("segment", x = -0.5, xend = -0.9, y = 0.85, yend = 0.85, 
             arrow = arrow(length = unit(0.1, "cm")), size = .5) +
    annotate("segment", x = 2.25, xend = 2.65, y = 0.85, yend = 0.85, 
             arrow = arrow(length = unit(0.1, "cm")), size = .5) +
    annotate("text", x = -0.5, y = 0.95, size = 2.75, label = "Less similar") +
    annotate("text", x = 2.15, y = 0.95, size = 2.75, label = "More similar") +
    labs(x = "Phonological similarity\n(Levenshtein, SD)", y = "P(Correct)", 
         colour = "PTHN", fill = "PTHN", linetype = "PTHN",
         title = "Population-level predictions") +
    scale_color_manual(values = c("#1E88E5", "#ff2976")) +
    scale_y_continuous(
        labels = function(x) percent(round(x, 2)),
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
    ) +
    theme(
        legend.position = "top",
        plot.title = element_blank()
    )

@@

## Accuracy

### Accuracy by item

```{r accuracy_item, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
responses_item <- responses %>%
    group_by(group, word) %>%
    summarise(
        correct_sum = sum(correct, na.rm = TRUE),
        correct_n = sum(!is.na(correct), na.rm = TRUE),
        .groups = "drop"
    ) %>% 
    mutate(
        correct_prop = prop_adj(correct_sum, correct_n),
        correct_se = prop_adj_se(correct_sum, correct_n),
        word_label = reorder_within(word, by = correct_prop, within = group)
    )

ggplot(responses_item, aes(reorder(word_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
    facet_wrap(~group, scales = "free_y") +
    geom_hline(yintercept = 0.5, colour = "black") +
    geom_errorbar() +
    geom_point(size = 0.5) +
    labs(y = "Correct responses", x = "Word", colour = "Group") +
    coord_flip() +
    scale_color_manual(values = c("#1A85FF", "#ff2976", "#FFC20A"), na.translate = FALSE) +
    scale_y_continuous(limits = c(0, 1), labels = percent) +
    theme(
        legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(size = 9),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
    )

### Accuracy by participant

```{r responses_participant, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
responses_participant <- responses %>%
    group_by(group, participant) %>%
    summarise(
        correct_sum = sum(correct, na.rm = TRUE),
        correct_n = sum(!is.na(correct), na.rm = TRUE),
        .groups = "drop"
    ) %>% 
    mutate(
        correct_prop = prop_adj(correct_sum, correct_n),
        correct_se = prop_adj_se(correct_sum, correct_n),
        participant_label = reorder_within(participant, by = correct_prop, within = group)
    )

ggplot(responses_participant, aes(reorder(participant_label, correct_prop), correct_prop, ymin = correct_prop-correct_se, ymax = correct_prop+correct_se, colour = group)) +
    facet_wrap(~group, scales = "free_y") +
    geom_hline(yintercept = 0.5) +
    geom_errorbar(width = 0.5) +
    geom_point(size = 1) +
    labs(
        y = "Correct responses",
        x = "Participant",
        colour = "Group"
    ) +
    coord_flip() +
    scale_color_manual(
        values = c("#1A85FF", "#ff2976", "#FFC20A"),
        na.translate = FALSE
    ) +
    scale_y_continuous(
        limits = c(0, 1), 
        labels = scales::percent
    ) +
    theme(
        legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(size = 9),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
    )

## Model diagnostics

```{r traceplots, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

posterior_draws_fixed %>% 
    mutate(
        .chain = as.factor(.chain),
        .variable_name = str_replace_all(.variable, str_repl) %>% 
            str_remove("b_")
    ) %>% 
    ggplot(aes(.iteration, .value, colour = .chain)) +
    facet_wrap(~.variable_name, scales = "free_y") +
    geom_line() +
    labs(x = "Iteration", y = "Value", color = "Chain") +
    scale_colour_manual(values = c("#1A85FF", "#ff2976", "#FFC20A", "04bf78"), na.translate = FALSE) +
    theme(legend.position = "top")

>>>>

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      median = ~median(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_median:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_median", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_median = md("Median"),
    frequency_sd = md("*SD*"),
    frequency_zipf_median = md("Median"),
    frequency_zipf_sd = md("*SD*"),
    pthn_median = md("Median"),
    pthn_sd = md("*SD*"),
    lv_median = md("Median"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("median"), -matches("lv")),
    fns = list(
      Median = "median",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Median = "median",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  )

@@

participants_valid %>% 
  count(group, l2, .drop = FALSE) %>% 
  mutate(
    l2 = case_when(
      l2=="Alemã\u0081n" ~ "German",
      l2=="Francã\u2030s" ~ "French",
      l2=="Cuã\u0081l" ~ "Missing",
      TRUE ~ l2
    ),
  ) %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot(aes(group, n, fill = l2)) +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_col(position = position_fill()) +
  labs(x = "L2", y = "# participants", fill = "L2") +
  scale_y_continuous(labels = percent) +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    strip.text = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank()
  )

@@

ggplot(
  post_re,
  aes(
    .value,
    reorder(as.factor(word), .value)
  )
) +
  geom_vline(
    xintercept = fixed_intercept[1],
    colour = "grey", 
    size = 1
  ) +

  stat_interval(
    size = 1.5,
    .width = c(0.5, 0.67, 0.95)
  ) +
  annotate(
    geom = "text",
    x = 0.7,
    y = 100,
    size = 3,
    hjust = 0.5,
    label = "Item accuracy \n(95%, 67%, and 50% CrI \nof item-level intercepts)"
  ) +
  annotate(
    geom = "rect",
    alpha = 0.15,
    xmin = fixed_intercept[2],
    xmax = fixed_intercept[3],
    ymin = -Inf,
    ymax = Inf
  ) +
  annotate(
    x = 0.7,
    xend = 0.6,
    y = 108,
    yend = 130,
    geom = "curve",
    curvature = 0.25,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  annotate(
    geom = "text",
    x = 0.8,
    y = 10,
    size = 3,
    hjust = 0.5,
    label = "Global posterior accuracy\n(Mean ± 95% CrI of the \npopulation-level intercept)"
  ) +
  annotate(
    x = 0.7,
    xend = fixed_intercept[1]+0.05,
    y = 17,
    yend = 30,
    geom = "curve",
    curvature = 0.2,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  labs(
    x = "Posterior probability of correct response",
    y = "Item",
    colour = "Credible Interval (CrI)",
    caption = "Credible intervals cover the range of values of the sampling space that \ncontain the true value with a given certainty."
  ) +
  scale_color_manual(
    values = c("#d2e5fc", "#9ccaff", "#1A85FF"),
    na.translate = FALSE, 
    labels = paste0(c(95, 67, 50), "%")
  ) +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme(
    legend.position = c(0.1, 0.9),
    legend.direction = "vertical",
    legend.justification = "left",
    legend.key = element_rect(fill = NA, colour = NA),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 5, hjust = 1),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    plot.caption.position = "plot",
    plot.caption = element_text(size = 9, hjust = 0, face = "plain", margin = margin(t = unit(3, "cm")))
  )

@@

```{r post_re_word_empirical, echo=FALSE, fig.height=9, fig.width=7, message=FALSE, warning=FALSE, paged.print=FALSE}

means <- responses %>% 
  group_by(group) %>% 
  summarise(
    successes = sum(correct, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    prop = prop_adj(successes, n),
    prop_se = prop_adj_se(successes, n)
  )

responses %>% 
  mutate(
    stim = paste0(
      word, " (", ipa1, ") / ", 
      word2, " (", ipa2, ") / ",
      percent(lv, accuracy = 1)
    )
  ) %>% 
  group_by(group, stim, lv) %>% 
  summarise(
    successes = sum(correct, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  mutate(
    prop = prop_adj(successes, n),
    prop_se = prop_adj_se(successes, n)
  ) %>% 
  ggplot() +
  aes(
    x = prop,
    y = reorder(as.factor(stim), lv),
    xmin = prop-prop_se,
    xmax = prop+prop_se,
    label = percent(lv),
    colour = group
  ) +
  facet_wrap(~group, scales = "free_y") +
  geom_vline(
    data = means,
    aes(xintercept = prop),
    size = 1,
    colour = "grey"
  ) +
  geom_errorbar(width = 0.1) +
  geom_point() +
  annotate(
    geom = "text",
    x = 0.7,
    y = 10,
    size = 3,
    hjust = 0.5,
    label = "Item accuracy \n(95% CI)"
  ) +
  annotate(
    x = 0.7,
    xend = 0.15,
    y = 13,
    yend = 20,
    geom = "curve",
    curvature = 0.25,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  # annotate(
  #   geom = "text",
  #   x = 0.8,
  #   y = 10,
  #   size = 3,
  #   hjust = 0.5,
  #   label = "Global posterior accuracy\n(Mean ± 95% CrI of the \npopulation-level intercept)"
  # ) +
  # annotate(
  #   x = 0.7,
  #   xend = fixed_intercept[1]+0.05,
#   y = 17,
#   yend = 30,
#   geom = "curve",
#   curvature = 0.2,
#   arrow = arrow(length = unit(0.2, "cm"))
# ) +
labs(
  x = "Probability of correct response",
  y = "Presented word / Correct translation / Levenshtein similarity"
) +
  scale_colour_manual(
    values = c("#1A85FF", "#ff2976", "#FFC20A"),
    na.translate = FALSE
  ) +
  scale_x_continuous(
    limits = c(0, 1), 
    labels = percent
  ) +
  theme(
    legend.position = "none",
    legend.direction = "vertical",
    legend.justification = "left",
    legend.key = element_rect(fill = NA, colour = NA),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 5, hjust = 1),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    plot.caption.position = "plot",
    plot.caption = element_text(size = 9, hjust = 0, face = "plain", margin = margin(t = unit(3, "cm")))
  )

ggsave(here("img", "accuracy_empirical.png"), height = 9, width = 15, dpi = 500)
```

@@

```{r marginaleffects, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.width=7, fig.height=3.5, fig.cap="Expected mean posterior predictions from Model 4. A) Population-level predictions: the X-axis and the Y-axis represent the PTHN score (in standard deviations from the mean) and the probability of correct translation, respectively. We simulated 300 observations from the posterior distribution of the model: 100 simulations for translations with no similarity (0% Levenshtein), 100 simulations for translations with mean accuracy (20.51% Levenshtein), and 100 simulations for translations with the maximum observed accuracy (83.33% Levenshtein). We did this across the range of values of the PTHN scores. For each simulation, we drew a single sample from the posterior distribution of each coefficient. Each simulation is depicted in the graph as a line: pink for minimum similarity translations, blue for hight similarity translations, and yellow for maximum similarity translations. Black, thick lines indicate the expected mean value of the posterior predictions of the model for each condition. The dispersion of the lines indicates the uncertainty of our predictions. We computed these posterior predictions for each group of participants, and plot tem in separate panels."}

nd <- expand.grid(
	lv_std = c(
		min(fit_6$data$lv_std),
		0,
		max(fit_6$data$lv_std)
	),
	frequency_zipf_std = 0,
	pthn_std = seq(
		min(fit_6$data$pthn_std, na.rm = TRUE),
		max(fit_6$data$pthn_std, na.rm = TRUE),
		by = 0.1
	),
	group = unique(fit_6$data$group)
)

m <- add_epred_draws(
	nd, 
	fit_6, 
	ndraws = 100, 
	re_formula = NA
) %>% 
	mutate(
		lv_std = factor(
			lv_std,
			levels = c(
				min(fit_6$data$lv_std),
				0,
				max(fit_6$data$lv_std)
			),
			labels = c(
				paste0("-1 SD (", percent(min(responses$lv, na.rm = TRUE)), ")"),
				paste0("Mean (", percent(mean(responses$lv, na.rm = TRUE)), ")"),
				paste0("+1 SD (", percent(max(responses$lv, na.rm = TRUE)), ")")
			)
		) 
	)

ggplot(m) +
	aes(
		pthn_std, 
		.epred,
		colour = lv_std,
		fill = lv_std
	) +
	facet_wrap(~group) +
	geom_hline(
		yintercept = 0.5, 
		colour = "grey"
	) +
	geom_line(
		aes(group = interaction(lv_std, .draw)), 
		size = 0.65,
		alpha = 0.5,
		show.legend = TRUE
	) +
	stat_summary(
		aes(linetype = lv_std), 
		fun = mean, 
		geom = "line",
		colour = "black", 
		size = 0.75,
		show.legend = TRUE
	) +
	annotate(
		"segment", 
		x = -0.5, 
		xend = -0.9, 
		y = 0.85, 
		yend = 0.85, 
		arrow = arrow(length = unit(0.1, "cm")), 
		size = .5
	) +
	annotate(
		"segment", 
		x = 2.25, 
		xend = 2.65, 
		y = 0.85, 
		yend = 0.85, 
		arrow = arrow(length = unit(0.1, "cm")),
		size = .5
	) +
	annotate(
		"text", 
		x = -0.5, 
		y = 0.95, 
		size = 2.75,
		label = "Less similar"
	) +
	annotate(
		"text", 
		x = 2.15, 
		y = 0.95, 
		size = 2.75,
		label = "More similar"
	) +
	labs(
		x = paste0("PTHN (+1 SD, ", round(sd(responses$pthn), 1), " higher-frequency neighbours)"),
		y = "P(Correct)", 
		colour = "Levenshtein similarity",
		fill = "Levenshtein similarity",
		linetype = "Levenshtein similarity",
		title = "Population-level posterior predictions"
	) +
	scale_y_continuous(
		labels = function(x) percent(round(x, 2)),
		limits = c(0, 1),
		breaks = seq(0, 1, 0.1)
	) +
	theme(
		legend.position = "top",
		plot.title = element_blank()
	)

@@
